Incentivizing Exploration with Unbiased History

### 2018-10-24 2level.tex
leveling
stuff
refactoring

%!TEX root = main.tex
\section{Warm-up:  Explore-then-Exploit Policy}
\swedit{Now we provide a simple policy that can incentivize the agents
  to perform non-adaptive exploration and achieve a regret rate of
  $\tilde O(T^{2/3})$. The policy essentially follows the
  ``explore-then-exploit'' paradigm and consists two phases, which can
  be described as a two-level information graph (as shown in
  Figure~\ref{fig:2level}).  In the first level, we perform
  exploration by simulating $T_1$ independent runs \ALGG of $\GdT$
  rounds. This is done by randomly dividing the first $T_1 \cdot \GdT$
  agents into $T_1$ groups of equal size and each agent only observe
  the history of all previous agents in the same group.  In the second
  level, we ``exploit'' by showing all the remaining agents the entire
  history of first phase.

@@

\caption{Structure of information graph for the 2-level policy. Each
  red ``box'' is level 1 corresponds to a path connecting a set of
  $T_G$ agents. The entire history in level 1 is then aggregated and
  shown to each agent in level 2.}
\label{fig:2level}
\end{figure}

@@

% \begin{itemize}
  \paragraph{Concentration of the number of arm $a$ pulls in the first
    level.}
  For each arm $a$, define $q_a$ to be the expected number of arm $a$
  pulls in a single run of \ALGG used in the first level.  By Lemma
  \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. Define $W_1^a$
  to be the event that the number of arm $a$ pulls in the first level
  is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.  \swedit{As long as
    we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$, this implies that
    the number of arm $a$ pulls is then at least $q_a T_1/2$.}  By
  Chernoff bound,
  \[
    \Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
  \]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\paragraph{Concentration of the empirical mean of arm $a$ pulls in the first level.}
To facilitate our reasoning, let us imagine there is a tape of length
$T$ for each arm $a$, with each cell containing an independent draw of
the realized reward from the distribution Ber$(\mu_a)$. Then for each
arm $a$ and any $N\in [T]$, we can think of the sequence of the first
$N$ realized rewards of $a$ coming from the prefix of $N$ cells in its
reward tape. Define $W^{a,t}_2$ to be the event that the empirical
mean of the first $t$ \swedit{realized rewards in the tape} of arm $a$
is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$
to be the intersection of these events (i.e.
$\bigcap_{a,t} W^{a,t}_2$).  By Chernoff bound,\swcomment{$t$ may be
  confusing here}
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound, 
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]

>>>>

%!TEX root = main.tex
\section{Warm-up:  2-Level Explore-then-Exploit Policy}
\swedit{Now we provide a simple policy that can incentivize the agents
  to perform non-adaptive exploration and achieve a regret rate of
  $\tilde O(T^{2/3})$. The policy essentially follows the
  ``explore-then-exploit'' paradigm and consists two phases, which can
  be described as a two-level information graph (as shown in
  Figure~\ref{fig:2level}).  In the first level, we perform
  exploration by simulating $T_1$ independent runs \ALGG of $\GdT$
  rounds. This is done by randomly dividing the first $T_1 \cdot \GdT$
  agents into $T_1$ groups of equal size and each agent only observe
  the history of all previous agents in the same group.  In the second
  level, we ``exploit'' by showing all the remaining agents the entire
  history of first phase.

@@

\caption{Structure of information graph for the 2-level policy. Each
  red ``box'' in level 1 corresponds to a path connecting a set of
  $T_G$ agents. The entire history in level 1 is then aggregated and
  shown to each agent in level 2.}
\label{fig:2level}
\end{figure}

@@

% \begin{itemize}
  \paragraph{Concentration of the number of arm $a$ pulls in the first
    level.}
  By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. Define
  $W_1^a$ to be the event that the number of arm $a$ pulls in the
  first level is at least $q_a T_1- \GdT \sqrt{T_1\log(T)}$.
  \swedit{As long as we set $T_1 \geq \frac{4\GdT^2}{\GdP^2}\log(T)$,
    this implies that the number of arm $a$ pulls is then at least
    $q_a T_1/2$.}  By Chernoff bound,
  \[
    \Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
  \]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\paragraph{Concentration of the empirical mean of arm $a$ pulls in the first level.}
To facilitate our reasoning, let us imagine there is a tape of length
$T$ for each arm $a$, with each cell containing an independent draw of
the realized reward from the distribution Ber$(\mu_a)$. Then for each
arm $a$ and any $N\in [T]$, we can think of the sequence of the first
$N$ realized rewards of $a$ coming from the prefix of $N$ cells in its
reward tape. Define $W^{a,t}_2$ to be the event that the empirical
mean of the first $t$ \swedit{realized rewards in the tape} of arm $a$
is at most $\sqrt{\frac{2\log(T)}{t}}$ away from $\mu_a$. Define $W_2$
to be the intersection of these events (i.e.
$\bigcap_{a,t} W^{a,t}_2$).  By Chernoff bound,\swcomment{$t$ may be
  confusing here}
\[
\Pr[W^{a,t}_2] \geq 1 - 2\exp(-4\log(T)) \geq 1-2/T^4.
\]
By union bound, 
\[
\Pr[W_2] \geq 1 - KT \cdot \frac{2}{T^4} \geq 1 - \frac{2}{T}.
\]

### 2018-10-24 3level.tex
refactoring

@@

Before we start with the case analysis, we first define several clean events and show that the intersection of them happens with high probability. 
\begin{itemize}
\item \textbf{Concentration of the number of arm $a$ pulls in the first level:} 
\swcomment{can we reuse the previous result?}
For $a \in \{1,2\}$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level. By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. For the $s$-th first-level group, define $W_1^{a,s}$ to be the event that the number of arm $a$ pulls in the $s$-th first-level group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Chernoff bound,
\[
\Pr[W_1^{a,s}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{4S}{T^2}.
\]
\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}
\swcomment{reusable?}
For each first-level group and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in this group pull arm $a$. For the $s$-th first-level group and arm $a$, define $W_2^{s,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away from $\mu_a$. By Chernoff bound, 
\[
\Pr[W_2^{s,a,t_1,t_2}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
\]

>>>>

\begin{lemma}[``Clean'' events]

\end{lemma}

@@

Before we start with the case analysis, we first define several clean events and show that the intersection of them happens with high probability. 
\begin{itemize}
\item \textbf{Concentration of the number of arm $a$ pulls in the first level:} 
By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. For the $s$-th first-level group, define $W_1^{a,s}$ to be the event that the number of arm $a$ pulls in the $s$-th first-level group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Chernoff bound,
\[
\Pr[W_1^{a,s}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{4S}{T^2}.
\]
\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}
\swcomment{reusable?}
For each first-level group and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in this group pull arm $a$. For the $s$-th first-level group and arm $a$, define $W_2^{s,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away from $\mu_a$. By Chernoff bound, 
\[
\Pr[W_2^{s,a,t_1,t_2}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
\]
